04_DESeq_sexes

### 2019-05-25 analysis/04_DESeq2_sexes.Rmd
pca violins

```{r plotpca, fig.dim = c(12, 10), eval=T}
p1 <- plotPCAs(pcas.female_hypothalamus, "female hypothalamus") 
p2 <- plotPCAs(pcas.female_pituitary, "female pituitary")   
p3 <- plotPCAs(pcas.female_gonad, "female gonad") 
p4 <- plotPCAs(pcas.male_hypothalamus, "male hypothalamus") 
p5 <- plotPCAs(pcas.male_pituitary, "male pituitary") 
p6 <- plotPCAs(pcas.male_gondad, "male gonad") 
p1 + theme_noaxislabels
p2 + theme_noaxislabels
p3 + theme_noaxislabels
p4 + theme_noaxislabels
p5 + theme_noaxislabels
p6 + theme_noaxislabels
```
```{r temp, eval = F}
mylegend <- get_legend(p1)

allPC1s <- plot_grid(p1 + theme_noaxislabels, 
                     p2 + theme_noaxislabels, 
                     p3 + theme_noaxislabels,
                     p4 + theme_noaxislabels,
                     p5 + theme_noaxislabels,
                     p6 + theme_noaxislabels,
                     nrow = 3, rel_heights = c(0.3, 0.3, 0.4))

pc1 <- plot_grid(allPC1s,mylegend,  nrow = 2, rel_heights = c(1.0, 0.15))
pc1

pdf("../figures/sexes/pca-1.pdf", width = 12, height = 10)
plot(pc1)
dev.off()
```

>>>>

```{r plotpca, fig.dim = c(12, 10), eval=T}
p1 <- plotPCAs(pcas.female_hypothalamus, "female hypothalamus") 
p2 <- plotPCAs(pcas.female_pituitary, "female pituitary")   
p3 <- plotPCAs(pcas.female_gonad, "female gonad") 
p4 <- plotPCAs(pcas.male_hypothalamus, "male hypothalamus") 
p5 <- plotPCAs(pcas.male_pituitary, "male pituitary") 
p6 <- plotPCAs(pcas.male_gondad, "male gonad") 
p1 + theme_noaxislabels
p2 + theme_noaxislabels
p3 + theme_noaxislabels
p4 + theme_noaxislabels
p5 + theme_noaxislabels
p6 + theme_noaxislabels

```
```{r pca, eval = T}
mylegend <- get_legend(p1)

allPC1s <- plot_grid(p1 + theme_noaxislabels + ylim(c(-40,40)), 
                     p4 + theme_noaxislabels + ylim(c(-40,40)), 
                     p2 + theme_noaxislabels + ylim(c(-40,40)),
                     p5 + theme_noaxislabels + ylim(c(-40,40)),
                     p3 + theme_nolegend + ylim(c(-40,40)) ,
                     p6 + theme_nolegend + ylim(c(-40,40)) ,
                     ncol = 2)

pc1 <- plot_grid(allPC1s, mylegend,  nrow = 2, rel_heights = c(1.0, 0.15))
pc1

pdf("../figures/sexes/pca-1.pdf", width = 12, height = 10)
plot(pc1)
dev.off()

```
